---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# macro_dashboard_data

<!-- badges: start -->

![refresh-data status](https://github.com/grattan/macro_dashboard_data/workflows/refresh-data/badge.svg)

<!-- badges: end -->

# About this repo
This repository contains various Australian macroeconomic data, along with the scripts needed to update that data. The scripts are set to execute daily via GitHub Actions, which updates the data.

The data is used by the Grattan macro dashboard.

-   [Dashboard repo](https://github.com/grattan/macrodashboard)

-   [Live dashboard](https://mattcowgill.shinyapps.io/macrodashboard/)

# Updates to this repo

The table below provides information about when the data in this repository was last updated.

```{r, include=FALSE}

last_run <- readLines(here::here("last_refreshed.txt"))

last_run <- lubridate::with_tz(last_run, "Australia/Melbourne")

last_updated <- readr::read_csv(here::here("last_updated.csv"))

last_updated$date <- lubridate::with_tz(last_updated$date, "Australia/Melbourne")

last_updated <- last_updated[rev(order(last_updated$date)),]

```

Data update script last run at `r last_run` AEST.

Data last updated at: `r knitr::kable(last_updated)`
